A Data-Driven Approach to Power Converter Control via Convex Optimization

### 2017-02-27 Papers/Loop Shaping Voltage Loop (CERN)/Latex/Draft_2/Draft_2.tex
updated files

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(k) &:= k_iP_1H;  &H_2(k) &:= k_uP_2e^{-j\omega \tau_{a}} \\
G &:= G_0e^{-j\omega\tau}; &C_m(k) &:= k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}\\ 
\end{aligned}
\end{equation}
where $k = [k_i,k_u,k_{m_1},k_{m_2}]$. Let the FRF from $v_d$ to $v_0$ be denoted as $T^{\prime}(k)$ and the FRF from $v_r$ to $v_0$ be denoted as $T(k)$. These closed-loop FRFs can easily be derived as follows:

\begin{align}
T^{\prime}(k) &= \frac{G(1+k_u)}{1+G[H_1(k)+H_2(k)]} \label{eq:Tclp}  \\ 
T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+e^{-\tau_{a}s} P_2C_m(k)]}  \label{eq:Tcl} 
\end{align}

@@

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
\begin{equation} 
\begin{aligned}
w(k) &= G[1+k_u+C_m(k)] \\
z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)]
\end{aligned}
\end{equation}
where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:
$$
\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
$$

Note that this constraint has the exact form as in (\ref{eq:con_cav}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the model-reference optimization problem as follows:
\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.

@@

The following properties will be needed in order to properly analyze the stability conditions of the system:
\begin{definition}
Let \emph{wno}$\{ A(s)\}$ refer to the winding number around the origin, in the counterclockwise sense, of the image of $A(s)$  when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis). Then the following properties hold:
\begin{align}
\emph{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \emph{wno}\bigl\{ A_1(s) \bigr\} + \emph{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
\end{align}
\end{definition}
The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)].$$ Let $F(k) = H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of right-half plane (RHP) poles of $G$ and $F$). The Nyquist plot of $1+GF$ must also not pass through the origin.

\begin{theorem} \label{Thm1}
Suppose that $k_i$, $k_u$, $k_{m_1}$, and $k_{m_2}$ are feasible solutions to the following constraint:
\begin{equation} \label{eq:theorem1_cond}
\begin{split}
z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \qquad 
\forall \omega \in \Omega
\end{split}
\end{equation}
where 
\begin{align*}
z(k) &= 1+G[H_1(k)+H_2(k)+e^{-j\omega \tau_{a}}P_2C_m(k)] \\
z_0 &= 1+G[H_1(k_0)+H_2(k_0)+e^{-j\omega \tau_{a}}P_2C_m(k_0)]
\end{align*}
with $\{G,H_1,H_2,P_2\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
\end{theorem}

\textit{Proof:}
The proof is based on the Nyquist stability criterion and the properties of the winding number. The winding number of $z^{\star}(k)z_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
{\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
&= -{\mbox{wno}} \{ 1+GF(k)\} \\
&\phantom{=} + {\mbox{wno}} \{ 1+GF(k_0)\} \\
\end{aligned}
\end{equation}
where $F(k_0) = H_1(k_0) + H_2(k_0) + e^{-\tau_{a}s}P_2 C_m(k_0)$. Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour. Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin. Therefore, $\mbox{wno} \{ z^{\star}(k)z_0\} = 0$; from (\ref{eq:winding_proof}), the following condition can then be realized:
\begin{equation} \label{eq:winding_proof3}
\mbox{wno} \{ 1+GF(k)\} = {\mbox{wno}} \{ 1+GF(k_0)\}
\end{equation}
The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $GF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
{\hfill \ensuremath{\blacksquare}}

>>>>

In order to simplify the system framework, let us define the following quantities:
\begin{equation} \label{eq:new_var}
\begin{aligned}
k_{m_1} &:= k_{p_1}(1+k_u) ;  &k_{m_2} &:= k_{p_2}(1+k_u)  \\
H_1(k) &:= k_iP_1H;  &H_2(k) &:= k_uP_2e^{-j\omega \tau_{a}} \\
H_3(k) &:=  P_2C_m(k)e^{-j\omega\tau_{a}}; &G &:= G_0e^{-j\omega\tau} \\ 
\end{aligned}
\end{equation}
\begin{equation*}
C_m(k) := k_{m_1}+k_{m_2}\frac{t_se^{-j\omega}}{1-e^{-j\omega}}
\end{equation*}
where $k = [k_i,k_u,k_{m_1},k_{m_2}]$. Let the FRF from $v_d$ to $v_0$ be denoted as $T^{\prime}(k)$ and the FRF from $v_r$ to $v_0$ be denoted as $T(k)$. These closed-loop FRFs can easily be derived as follows:

\begin{align}
T^{\prime}(k) &= \frac{G(1+k_u)}{1+G[H_1(k)+H_2(k)]} \label{eq:Tclp}  \\ 
T(k) &= \frac{G[1+k_u+C_m(k)]}{1+G[H_1(k)+H_2(k)+H_3(k)]}  \label{eq:Tcl} 
\end{align}

@@

 \begin{equation} \label{eq:min_loopshape}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}}
& & \gamma  \\
& \text{subject to:} & & \bigl[T(k)-T_d\bigr]^{\star}\bigl[T(k)-T_d\bigr] < \gamma
\end{aligned}
\end{equation}
for all $\omega \in \Omega$. It can be observed that the constraint in (\ref{eq:min_loopshape}) is not convex. Let us now define the following quantities:
\begin{equation} 
\begin{aligned}
w(k) &= G[1+k_u+C_m(k)] \\
z(k) &= 1+G[H_1(k)+H_2(k)+H_3(k)]
\end{aligned}
\end{equation}
where it is evident that $T(k) = w(k)z^{-1}(k)$; then the constraint in (\ref{eq:min_loopshape}) can be written as:
$$
\bigl[w(k)-z(k)T_d \bigr]^{\star}\gamma^{-1} \bigl[w(k)-z(k)T_d \bigr] - z^{\star}(k)z(k)<0
$$

Note that this constraint has the exact form as in (\ref{eq:con_cav}); therefore, the convex constraint in (\ref{eq:LMI_1}) can be utilized to construct the model-reference optimization problem as follows:
\begin{equation} \label{eq:loop_shape_LMI_inf}
\begin{aligned}
& \underset{ k \in \mathbb{R}}{\text{minimize}} \hspace{0.5cm} \gamma  \\
& \text{subject to:} \\
&
\begin{bmatrix}
z^{\star}(k)z_0 + z_0^{\star}z(k) - z_0^{\star}z_0 & \phantom{xx}[w(k)-z(k)T_d]^{\star} \\ 
w(k)-z(k)T_d & \phantom{xx}\gamma
\end{bmatrix} \succ 0
\end{aligned}
\end{equation}
for all $\omega \in \Omega$, where $$z_0 = 1+G[H_1(k_0) + H_2(k_0)+H_3(k_0)]$$ and $k_0 =[k_{i,0},k_{u,0},k_{m_1,0},k_{m_2,0}  ]$ are the initializing gains.

@@

The following properties will be needed in order to properly analyze the stability conditions of the system:
\begin{definition}
Let \emph{wno}$\{ A(s)\}$ refer to the winding number around the origin, in the counterclockwise sense, of the image of $A(s)$  when $s$ traverses the Nyquist contour (with small detours around the poles of $A(s)$ on the imaginary axis). Then the following properties hold:
\begin{align}
\emph{wno}\bigl\{ A_1(s)A_2(s) \bigr\} &= \emph{wno}\bigl\{ A_1(s) \bigr\} + \emph{wno}\bigl\{ A_2(s) \bigr\}  \label{eq:wno_add}\\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{\star}(s)\bigr\} \label{eq:wno_conj} \\ 
\emph{wno}\bigl\{ A(s)\bigr\} &= -\emph{wno}\bigl\{ A^{-1}(s)\bigr\} \label{eq:wno_inv}
\end{align}
\end{definition}
The open-loop FRF of the system $T(k)$ in Fig.~\ref{fig:damping_loop} is given as $$L(k) = G[H_1(k)+H_2(k)+H_3(k)].$$ Let $F(k) = H_1(k)+H_2(k)+H_3(k)$ such that $L(k) = GF(k)$; by the Nyquist stability criterion, the closed-loop system is stable if and only if $1+GF$ makes $n_{G}+n_F$ counter-clockwise encirclements of the origin (where $n_{G}$ and $n_F$ are, respectively, the number of right-half plane (RHP) poles of $G$ and $F$). The Nyquist plot of $1+GF$ must also not pass through the origin.

\begin{theorem} \label{Thm1}
Suppose that $k_i$, $k_u$, $k_{m_1}$, and $k_{m_2}$ are feasible solutions to the following constraint:
\begin{equation} \label{eq:theorem1_cond}
\begin{split}
z^{\star}(k)z_0+z_0^{\star}z(k) > 0 \qquad 
\forall \omega \in \Omega
\end{split}
\end{equation}
where 
\begin{align*}
z(k) &= 1+G[H_1(k)+H_2(k)+H_3(k)] \\
z_0 &= 1+G[H_1(k_0)+H_2(k_0)+H_3(k_0)]
\end{align*}
with $\{G,H_1,H_2,H_3\} \in \mathscr{S}$. Then the closed-loop system $T$ is stable if the parameters in the set $k_0$ are stabilizing initial gains.
\end{theorem}

\textit{Proof:}
The proof is based on the Nyquist stability criterion and the properties of the winding number. The winding number of $z^{\star}(k)z_0$ is given as follows:
\begin{equation} \label{eq:winding_proof}
\begin{aligned}
{\mbox{wno}} \{ z^{\star}(k)z_0\} &= {\mbox{wno}} \{ z^{\star}\} + {\mbox{wno}} \{ z_0\} \\
&= -{\mbox{wno}} \{ 1+GF(k)\} \\
&\phantom{=} + {\mbox{wno}} \{ 1+GF(k_0)\} \\
\end{aligned}
\end{equation}
where $F(k_0) = H_1(k_0) + H_2(k_0) + H_3(k_0)$. Note that $F(k)$ is strictly proper and $GF(k)$ is strictly proper; therefore, the winding number of $z^{\star}(k)z_0$ can be evaluated over $\Omega$ instead of the $D$-contour. Additionally, the constraint in (\ref{eq:theorem1_cond}) implies that $\Re\{ z^{\star}(k)z_0\} > 0$ (where $\Re\{ \cdot \}$ indicates the real part of the argument), which signifies that the Nyquist plot of $z^{\star}(k)z_0$ will not pass through or encircle the origin. Therefore, $\mbox{wno} \{ z^{\star}(k)z_0\} = 0$; from (\ref{eq:winding_proof}), the following condition can then be realized:
\begin{equation} \label{eq:winding_proof3}
\mbox{wno} \{ 1+GF(k)\} = {\mbox{wno}} \{ 1+GF(k_0)\}
\end{equation}
The condition in (\ref{eq:winding_proof3}) implies that if the initializing controllers $k_0$ are stabilizing (i.e., the open-loop system $GF(k_0)$ meets the Nyquist stability criterion), then the closed-loop system will be stable.
{\hfill \ensuremath{\blacksquare}}
